---
title: 'p8105_hw1_nt2607'
output: github_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

data("penguins", package = "palmerpenguins")

### The penguins dataset can be viewed here: 
  
head(penguins)
```

## Problem 1

This problem focuses the use of inline R code, plotting, and the behavior of ggplot for variables of different types.

### Description of the penguins dataset 

The variable names of this dataset are : `r names(penguins)`.

This dataset contains information about different species of penguins on some island. Some important variables describing the physical traits of these penguins include `bill_length_mm` , `bill_depth_mm`, `flipper_length_mm`, `body_mass_g`, `sex` and `year`.

The size of the dataset : There are `r nrow (penguins)` rows and `r ncol (penguins)` columns in this dataset.

The mean flipper length is `r mean(pull(penguins,flipper_length_mm), na.rm = TRUE)`

### Scatterplot of `flipper_length_mm` vs `bill_length_mm`

```{r scatterplot_penguins}

penguins_df_plot = tibble(
  x = penguins$bill_length_mm,
  y = penguins$flipper_length_mm,
  species = penguins$species
)

ggplot(penguins_df_plot, aes(x = x, y = y, color = species)) + geom_point()

ggsave("scatter_plot.pdf", height = 4, width = 6)

```

## Problem 2

This problem is intended to emphasize variable types and introduce coercion; some awareness of how R treats numeric, character, and factor variables is necessary for working with these data types in practice.

```{r dataframe_2}

problem2_df = tibble(
  norm_samp = rnorm (10, mean = 0, sd = 1),
  vec_logical = norm_samp > 0,
  vec_char = c("a", "b", "c", "d", "e","f", "g", "h", "i", "j"),
  vec_fact = factor(c("low", "low","low", "med", "med", "med","high", "high", "high", "low"))
)

head(problem2_df)





```











